The title

### 2023-01-21 docs/draft/draft.Rmd
Cambios

The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.  
<!--- we might consider (not rn but to be discussed) deleted the "could not be physically present" part, it could open a can of worms---> 
Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it. 
<!--- I think the above sentence might be unnecessary bc we don't necessarily talk about communicative strategies --> 
Research and technological advances allowed online language education to develop greatly, <!--- for example, x, y, z helps students to do a, b, and c. then start with the next sentence--->  
However, the Covid-19 pandemic appeared to be its hardest challenge to date. <!--- in what way? are we saying covid was a challenge for online learning? this seems to go against the previous sentences saying that techology had advanced and online learning has developed-->
According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (*insert citation*). 
Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs. 6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs. 2.4 million).

Language attitudes are key in the language learning environment, as they can determine the success of a student [eg @thompson2021attitudes]. <!--- lets avoid statements that are very direct and assertive like that, something more like "they play a role in determining the success of a student ---> 
A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged (*insert citation*).
Interestingly, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [@alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using]. 
Within this framework <!---i'm not sure that framework is the right word here-->, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. 
<!--- i think this sentence should be deleted "Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment." --> 
<!--- i'm going to think about how to rework these examples into a paragraph that flows a little better Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. 
Their results showed an incremental fluctuation in their perception. 
That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. 
A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses. 
Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course. 
During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors. 
While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. 
Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. 
Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion]. --->

The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. 
<!--- This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. - maybe delete this ---> 
With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. <!--- idk if we can say "global decrease" maybe something like "with a push to return to pre-covid practices" ---> 
The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

<!--- i don't know if this paragraph is necessary "Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students. 
In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history." --->

@@

#### Effectiveness

@@

#### Perception / attitudes

@@

In order to study and understand tendencies in online learning, we turned to Grounded Theory, as it allows for a cyclical observation of a changing world, where the researcher is a constant observer of the changes produced [@hernandez2014investigacion]. 
This theoretical approach allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs. in-person language classes. 
Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them [@corbin2014basics]. <!--- can you elaborate on this? --->

>>>>

The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals.
<!--- we might consider (not rn but to be discussed) deleted the "could not be physically present" part, it could open a can of worms---> 
Of particular interest is the research and development of online language education along with technological advances that made possible an evolution in the quality and accessibility of the materials. 
For example, implementing online tools such as Zoom, VoiceThread, FlipGrid, etc, allowed students to hold conversations, share ideas and provide their opinions in a similar way to a traditional online setting.

According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses [@nationalstatistics_2022]. 
Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs. 6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs. 2.4 million).

<!--- I think the above sentence might be unnecessary bc we don't necessarily talk about communicative strategies --> 
<!--- IAR Two lines convined --> 
<!--- for example, x, y, z helps students to do a, b, and c. then start with the next sentence--->  
However, the Covid-19 pandemic appeared to be its hardest challenge to date, as many educators where not prepare for the online transition @tomasik2021educational. <!--- in what way? are we saying covid was a challenge for online learning? this seems to go against the previous sentences saying that techology had advanced and online learning has developed-->

The outbreak of COVID-19 has caused online teaching and learning to evolve rapidly during the past two years due to the national online swift. 
However, with the progressive decrease in global covid cases, universities are adopting a pre-pandemic approach, making students return to the educational classroom.

<!--- This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. - maybe delete this ---> 
With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. <!--- idk if we can say "global decrease" maybe something like "with a push to return to pre-covid practices" ---> 
The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and, second to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

<!--- i don't know if this paragraph is necessary "Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students. 
In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history."  -esto quizas entraria mejor como primera linea en "the current study"- --->

@@

In several decades of existence and development, online learning has never gained more attention than it did over the national pandemic, as 75 percent of undergraduate students were enrolled in at least one online course [@nationalstatistics_2022].
Previous pre-pandemic research has proven that distance students can archive similar learning goals as those students that were physically present on the educational environment [eg: @mccutcheon2015systematic, @means2013effectiveness, @sun2016online].
While online learning comes with a set of challenges that are not found in a traditional classroom, such as the ability to self-regulate, and the lack of interaction, it can improve the effectiveness and efficiency of education as it eliminates geographical barriers, improving accessibility, and the ability to learn at the student's pace [@kebritchi2017issues].

During the pandemic, one of the most cited difficulties with the quick transition to online education was the lack of preparation and families with educational tools.
Being forced to switch moralities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials.
[@mahyoob2020challenges] describes how both students and educators found technical problems concerning the use of technology, affecting the adequate distribution of teaching materials and communications among the students.
These difficulties faded as the teaching force became more familiar with the learning tools. 
In addition, the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials and therefore gained more experience with their newfound educational setting. 
[@ruiz2022transitioning]
Likewise, the attitudes toward the online setting evolved throughout the pandemic. Increased autonomy and self-paced learning opportunities offered by the new online format were overall the most liked attributes of the change.

#### Effectiveness and attitudes toward online education 
#Intro online learning history

Language attitudes are essential in the language learning environment, as they play an important role in determining the student's final success in the language course.
Similarly, a learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.[eg @thompson2021attitudes] <!--- lets avoid statements that are very direct and assertive like that, something more like "they play a role in determining the success of a student --->
Not surprisingly, the attitudes in online learning have been shown to play a fundamental role as students are physically detached from the learning environment, and rely more on self-regulation abilities [@alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using]. 
Within this line of research <!---i'm not sure that framework is the right word here-->, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. 
<!--- i think this sentence should be deleted "Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment." -como quieras, lo que queria era expresar la idea que a traves de la experiencia y ver el sistema, los niveles de ansiedad disminuyen - -->

@tophatfall2020 did a major survey on undergraduate students’ and teachers’ perceptions at the beginning of the online emergency switch in US universities. 
Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting. 
In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. 
Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.<!--- conexion con como progresivamente la situacion fue mejorando.

<!--- i'm going to think about how to rework these examples into a paragraph that flows a little better

Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. 
Their results showed an incremental fluctuation in their perception. 
That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. 
A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses. 
Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course. 
During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors. 
While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. 
Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. 
Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion]. --->

@@

With the decrease in covid cases, most major US universities are looking to transition into face-to-face settings, creating a new reality within language education. 
A global survey [@widenhorn2023comparing] of more than 5.000 university students revealed that more than four in five students (82%) would still want to have at least some of their courses online after having passed two years of the global pandemic. 
Similarly, two in five university students (41%) would still prefer to continue online without physical interaction with the educational classroom. 
When asked what factors other than the pandemic had an impact, students replied with the economy (73%), location or transportation (44%), and lack of access to technology (35%)
This is the most extensive study that tackles the shift toward face-to-face education after the online pandemic to date. 
However, this study is broad as it covers several countries with different economic needs and transportation necessities. 
Therefore, our study aims to provide more fine-grained detail about the post-pandemic tendencies in a North Eastern US university ....

@@

In order to study and understand tendencies in online learning, we turned to Grounded Theory, as it allows for a cyclical observation of a changing world, where the researcher is a constant observer of the changes produced [@hernandez2014investigacion]. 
This theoretical approach allows the research team to explain the relationships among categories within the same reality. 
It is a constant comparison methodology of data of the reality being studied, where the hypothesis are formulated throughout the research process. 
This was performed via student evaluations, which allowed to test the thematic coding structuration and check for unanticipated topics. 
In this step, the most noteworthy categories were selected (axial coding) with the intention of making a posterior analysis (selected coding). 
A Qualtrics Survey followed this initial observation, which allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs. in-person language classes. 
We then tested each category in... (add statisct analysis used).

Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within a specific area, along with the factors that affect them [@corbin2014basics].
Thus we understand that the results we obtain might be limited to the area from where the information is being extracted.  
Social factors such as distance from campus, commuting time, working hours, or access to the internet might be geographically dependent and not extrapolable to other areas or countries.

### 2023-01-21 docs/draft/draft.tex
Cambios

** big picture = social implications of online teaching and how that has changed in a post-pandemic world
** small picture = what we are doing in this language program and how can we improve to meet the needs and wants of the students in their new reality

\begin{itemize}
\item
  Address the general idea
\item
  Explain the study
\item
  Address our contribution
\end{itemize}

@@

\hypertarget{literature-review}{%
\section{Literature Review}\label{literature-review}}

The development of online education has been evolving over the past few decades, offering an alternative to deliver learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom. Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it. Research and technological advances allowed online language education to develop greatly, however, the Covid-19 pandemic appeared to be its hardest challenge to date. According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses. Compared to fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.~6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.~2.4 million).

Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually. Being forced to switch modalities had consequences, both from the teachers' and students' perspectives, as they were either not ready for the change or lacked many materials. Top Hat (2020) did a major survey on undergraduate students' and teachers' perceptions during the online emergency switch in US universities. Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting. In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.

Language attitudes are key in the language learning environment, as they can determine the success of a student (eg Thompson, 2021). A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged. Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi et al., 2016; Horvat, Dobrota, Krsmanovic, \& Cudanov, 2015; Ke \& Kwak, 2013; Lan \& Sie, 2010). Within this framework, anxiety has been linked in several research studies (e.g., Teimouri, Goetze, \& Plonsky, 2019) as an indicator of poor linguistic development. Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. Furthermore, Webb, Doman, and Pusey (2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese. Their results showed an incremental fluctuation in their perception. That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. A similar psychological development is observed in Ushida (2005) study which investigated the changes in students' attitudes and motivation over time in online language courses. Their results showed a similar evolution within the student's attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.~2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel and Ringeisen (2019)), which might involve some training and assistance before the beginning of the online course. During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Tomasik, Helbling, and Moser (2021), leading to an overall feeling of less effective education Top hat (2020), Hodges, Moore, Lockee, Trust, and Bond (2020), Lee (2022). While the immediate transition to online education seemed rushed in Ruiz-Alonso-Bartol, Querrien, Dykstra, Fernández-Mira, and Sánchez-Gutiérrez (2022) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments (Chakraborty, Mittal, Gupta, Yadav, \& Arora, 2021).
The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

\hypertarget{research-gap-and-theoretical-approach}{%
\section{Research gap and theoretical approach}\label{research-gap-and-theoretical-approach}}

Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students. In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history.

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment. To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world. The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernandez Carrera, 2014). Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

This theoretical approach allowed us to perform mixed models including qualitative, quantitative, and open questionary deriving the hypothesis we present in this paper. This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data. Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them (Corbin \& Strauss, 2014).

@@

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years.
The effects of this ever-changing learning environment have affected students and continue to affect modulating the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes, have brought a new educational reality that affects tendencies toward enrollment.
Having a better understanding of the constant change of tendencies that affect our students can help us not only in providing them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

@@

\leavevmode\vadjust pre{\hypertarget{ref-chakraborty2021opinion}{}}%
Chakraborty, P., Mittal, P., Gupta, M. S., Yadav, S., \& Arora, A. (2021). Opinion of students on online education during the COVID-19 pandemic. \emph{Human Behavior and Emerging Technologies}, \emph{3}(3), 357--365.

@@

\leavevmode\vadjust pre{\hypertarget{ref-heckel2019pride}{}}%
Heckel, C., \& Ringeisen, T. (2019). Pride and anxiety in online learning environments: Achievement emotions as mediators between learners' characteristics and learning outcomes. \emph{Journal of Computer Assisted Learning}, \emph{35}(5), 667--677.

@@

\leavevmode\vadjust pre{\hypertarget{ref-hodges2020difference}{}}%
Hodges, C. B., Moore, S., Lockee, B. B., Trust, T., \& Bond, M. A. (2020). \emph{The difference between emergency remote teaching and online learning}.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-lee2022factors}{}}%
Lee, S.-M. (2022). Factors affecting the quality of online learning in a task-based college course. \emph{Foreign Language Annals}, \emph{55}(1), 116--134.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-ushida2005role}{}}%
Ushida, E. (2005). The role of students' attitudes and motivation in second language learning in online language courses. \emph{CALICO Journal}, 49--78.

\leavevmode\vadjust pre{\hypertarget{ref-webb2014flipping}{}}%
Webb, M., Doman, E., \& Pusey, K. (2014). Flipping a chinese university EFL course: What students and teachers think of the model. \emph{The Journal of Asia TEFL}, \emph{11}(4), 53--87.

>>>>

The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals.
Of particular interest is the research and development of online language education along with technological advances that made possible an evolution in the quality and accessibility of the materials.
For example, implementing online tools such as Zoom, VoiceThread, FlipGrid, etc, allowed students to hold conversations, share ideas and provide their opinions in a similar way to a traditional online setting.

According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (Education Statistics, 2022).
Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.~6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.~2.4 million).

However, the Covid-19 pandemic appeared to be its hardest challenge to date, as many educators where not prepare for the online transition Tomasik, Helbling, and Moser (2021).

The outbreak of COVID-19 has caused online teaching and learning to evolve rapidly during the past two years due to the national online swift.
However, with the progressive decrease in global covid cases, universities are adopting a pre-pandemic approach, making students return to the educational classroom.

With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and, second to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

\hypertarget{previous-literature-and-theoretical-framework}{%
\section{Previous literature and theoretical framework}\label{previous-literature-and-theoretical-framework}}

The goal of the current paper is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years.
The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education.
Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.

\hypertarget{online-learning}{%
\subsection{Online learning}\label{online-learning}}

In several decades of existence and development, online learning has never gained more attention than it did over the national pandemic, as 75 percent of undergraduate students were enrolled in at least one online course (Education Statistics, 2022).
Previous pre-pandemic research has proven that distance students can archive similar learning goals as those students that were physically present on the educational environment Sun \& Chen (2016).
While online learning comes with a set of challenges that are not found in a traditional classroom, such as the ability to self-regulate, and the lack of interaction, it can improve the effectiveness and efficiency of education as it eliminates geographical barriers, improving accessibility, and the ability to learn at the student's pace (Kebritchi, Lipschuetz, \& Santiague, 2017).

During the pandemic, one of the most cited difficulties with the quick transition to online education was the lack of preparation and families with educational tools.
Being forced to switch moralities had consequences, both from the teachers' and students' perspectives, as they were either not ready for the change or lacked many materials.
(Mahyoob, 2020) describes how both students and educators found technical problems concerning the use of technology, affecting the adequate distribution of teaching materials and communications among the students.
These difficulties faded as the teaching force became more familiar with the learning tools.
In addition, the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials and therefore gained more experience with their newfound educational setting.
(Ruiz-Alonso-Bartol, Querrien, Dykstra, Fernández-Mira, \& Sánchez-Gutiérrez, 2022)
Likewise, the attitudes toward the online setting evolved throughout the pandemic. Increased autonomy and self-paced learning opportunities offered by the new online format were overall the most liked attributes of the change.

\hypertarget{effectiveness-and-attitudes-toward-online-education}{%
\paragraph{Effectiveness and attitudes toward online education}\label{effectiveness-and-attitudes-toward-online-education}}

\#Intro online learning history

Language attitudes are essential in the language learning environment, as they play an important role in determining the student's final success in the language course.
Similarly, a learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.(eg Thompson, 2021)
Not surprisingly, the attitudes in online learning have been shown to play a fundamental role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi et al., 2016; Horvat, Dobrota, Krsmanovic, \& Cudanov, 2015; Ke \& Kwak, 2013; Lan \& Sie, 2010).
Within this line of research , anxiety has been linked in several research studies (e.g., Teimouri, Goetze, \& Plonsky, 2019) as an indicator of poor linguistic development.

Hat (2021) did a major survey on undergraduate students' and teachers' perceptions at the beginning of the online emergency switch in US universities.
Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting.
In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students.
Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.

\hypertarget{motivation}{%
\paragraph{Motivation}\label{motivation}}

With the decrease in covid cases, most major US universities are looking to transition into face-to-face settings, creating a new reality within language education.
A global survey (Widenhorn, Hardy, Manuel, Botha, \& Robinson, 2023) of more than 5.000 university students revealed that more than four in five students (82\%) would still want to have at least some of their courses online after having passed two years of the global pandemic.
Similarly, two in five university students (41\%) would still prefer to continue online without physical interaction with the educational classroom.
When asked what factors other than the pandemic had an impact, students replied with the economy (73\%), location or transportation (44\%), and lack of access to technology (35\%)
This is the most extensive study that tackles the shift toward face-to-face education after the online pandemic to date.
However, this study is broad as it covers several countries with different economic needs and transportation necessities.
Therefore, our study aims to provide more fine-grained detail about the post-pandemic tendencies in a North Eastern US university \ldots.

\hypertarget{grounded-theory}{%
\subsection{Grounded theory}\label{grounded-theory}}

In order to study and understand tendencies in online learning, we turned to Grounded Theory, as it allows for a cyclical observation of a changing world, where the researcher is a constant observer of the changes produced (Hernandez Carrera, 2014).
This theoretical approach allows the research team to explain the relationships among categories within the same reality.
It is a constant comparison methodology of data of the reality being studied, where the hypothesis are formulated throughout the research process.
This was performed via student evaluations, which allowed to test the thematic coding structuration and check for unanticipated topics.
In this step, the most noteworthy categories were selected (axial coding) with the intention of making a posterior analysis (selected coding).
A Qualtrics Survey followed this initial observation, which allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs.~in-person language classes.
We then tested each category in\ldots{} (add statisct analysis used).

Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within a specific area, along with the factors that affect them (Corbin \& Strauss, 2014).
Thus we understand that the results we obtain might be limited to the area from where the information is being extracted.\\
Social factors such as distance from campus, commuting time, working hours, or access to the internet might be geographically dependent and not extrapolable to other areas or countries.

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-nationalstatistics_2022}{}}%
Education Statistics, N. C. for. (2022). Coe - undergraduate enrollment - national center for education statistics. U.S. Department of Education, Institute of Education Sciences. Retrieved from \url{https://nces.ed.gov/programs/coe/indicator/cha}

\leavevmode\vadjust pre{\hypertarget{ref-tophatfall2020}{}}%
Hat, T. (2021). Adrift in a pandemic: Survey of 3,089 students finds uncertainty about returning to college. Retrieved from \url{https://tophat.com/press-releases/adrift-in-a-pandemic-survey/}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-kebritchi2017issues}{}}%
Kebritchi, M., Lipschuetz, A., \& Santiague, L. (2017). Issues and challenges for teaching successful online courses in higher education: A literature review. \emph{Journal of Educational Technology Systems}, \emph{46}(1), 4--29.

@@

\leavevmode\vadjust pre{\hypertarget{ref-mahyoob2020challenges}{}}%
Mahyoob, M. (2020). Challenges of e-learning during the COVID-19 pandemic experienced by EFL learners. \emph{Arab World English Journal (AWEJ)}, \emph{11}(4).

\leavevmode\vadjust pre{\hypertarget{ref-mccutcheon2015systematic}{}}%
McCutcheon, K., Lohan, M., Traynor, M., \& Martin, D. (2015). A systematic review evaluating the impact of online or blended learning vs. Face-to-face learning of clinical skills in undergraduate nurse education. \emph{Journal of Advanced Nursing}, \emph{71}(2), 255--270.

\leavevmode\vadjust pre{\hypertarget{ref-means2013effectiveness}{}}%
Means, B., Toyama, Y., Murphy, R., \& Baki, M. (2013). The effectiveness of online and blended learning: A meta-analysis of the empirical literature. \emph{Teachers College Record}, \emph{115}(3), 1--47.

@@

\leavevmode\vadjust pre{\hypertarget{ref-sun2016online}{}}%
Sun, A., \& Chen, X. (2016). Online education and its effective practice: A research review. \emph{Journal of Information Technology Education}, \emph{15}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-widenhorn2023comparing}{}}%
Widenhorn, M., Hardy, D. W., Manuel, J. A., Botha, A., \& Robinson, R. (2023). Comparing global university mindsets and student expectations: Closing the gap to create the ideal learner experience. \emph{Available at SSRN 4320170}.
